WERTi - Easing Second Language Acquisition

### 2008-06-26 docs/paper/paper.tex
Post-Presentation commit
Various updates. WERTi will be restructured significantly this weekend.

\usepackage[english]{babel}
\usepackage{qtree}
\usepackage[utf8x]{inputenc}
\usepackage{linguex}

@@

@@

The current processing line can be split up into three different parts that can
interact autonomously themselves but each depend on the output of their
predecessor. The components are arranged in the following manner:

@@

\item[HTML processing:] annotates HTML tags, finds ``relevant'' text within the
tags.

\item[Linguistic processing:] performs linguistic tasks (tokenization, sentence
boundary detection, part-of-speech tagging\ldots{}) on the text-annoatations
from the previous processing step.

\item[Post processing:] Performs all sorts of content enhancement on the
annotations of the previous two processing steps.

@@

@@

The HTML processor method was designed to be primitive and efficient. While
using a fully capable HTML parser was considered, we preffered to use a more
simple approach since there didn't seem to be any need for the additional data
an HTML parser could have provided us with. Furthermore, changing the
implementation of an analysis step even this fundamental to further processing
should be easy and without side-effects as long as the requirements to
preconditions and postconditions are met.

\paragraph{Preconditions} We have a document represented as a singleton and
stored in the UIMA-CAS that is passed to the \verb#process(CAS)#-method of the
\verb#HTMLAnnotator#-class.

@@

@@

\section{The User Inteface}

@@

>>>>

\usepackage[english]{babel}
\usepackage{qtree}
\usepackage{aleks}
\usepackage[utf8x]{inputenc}
\usepackage{linguex}

@@

This section will explain the principles underlying WERTi's functionality by
first looking at the data processing architecture and then showing how this is
then integrated into the user interface of the web application.

@@

The current processing line can be split up into three different parts that can
interact autonomously but each depend on the output of their predecessor. The
components are arranged in the following order:

@@

\item[HTML processing:] annotates HTML tags, finds ``relevant'' text within the
tags. This lays ground to later linguistic analysis by setting the margins of
where the latter has to operate on in the web content.

\item[Linguistic processing:] performs linguistic tasks (tokenization, sentence
boundary detection, part-of-speech tagging\ldots{}) on the text-annotations
from the previous processing step. This is also the most intensive step from a
computational point of view. Optimizations to the code are most likely to yield
visible results here.

\item[Post processing:] Performs all sorts of content enhancement on the
annotations of the previous two processing steps. Note that this step depends on
both annotation results: it also needs certain HTML markups in order to
correctly organize all of the code that is going to be executed on client side.

@@

We will now go on and explain those steps in further detail.

@@

The HTML processor method was designed to be primitive and efficient. While
using a fully capable HTML parser was considered, we preferred to use a more
simple approach. Full and formally correct HTML markup was deemed unnecessary and
too time intensive.
Furthermore, changing the
implementation of an analysis step even this fundamental to further processing
should be easy and without side-effects as long as the requirements to
preconditions and postconditions are met.

\paragraph{Preconditions} We have a document represented as a singleton
String\footnote{As usual in UIMA. For large documents, UMIA provides ways of
splitting up documents and processing the chunks independently. However, UIMA
only considers documents well beyond one megabyte to be ``big enough'' to be
split and the plain HTML most web pages serve rarely exceeds this mark.}   and
stored in the UIMA-CAS that is passed to the \verb#process(CAS)#-method of the
\verb#HTMLAnnotator#-class.
\paragraph{Postconditions} The document contains annotations marking up the
positions and spans of html tags in the document text. The names of
tags\footnote{E.g. ``p'' for the tag \texttt{<p>} or ``div'' for the dag
\texttt{div}.} are
also stored and a \verb#isClosing#-flag is set, that denotes whether this tag is
closing another\footnote{A preceding slash in the tag name closes the tag.}.

@@

Linguistic processing goes through 3 major steps: \emph{Tokenization},
\emph{Sentence Boundary Detection}

@@

\section{The User Interface}

@@

\section{The Development Process}
In this section I want to display in what environment the project has been
written and what technologies have been put to use.

\subsection{Concept \& Design}
The original design of WERTi has been developed at Ohio State University by
\textsc{Detmar Meurers} and his research associates. There exist several papers
about this original work. At Tübingen University the concept has been extended
to

\subsection{Design Process} My Work on the Java implementation of WERTi was
mostly autonomous. I had been given free choice over the frameworks and
development environment I wanted to put to use, with the only exceptions being
being using \emph{Java} and the UIMA architecture to achieve maximum flexibility
and portability. Maximum flexibility and extensibility were the main goals of
the re-implementation.

Development happened in a very productive atmosphere with weekly project
meetings where core functionality and the design of the analysis process were
discussed. After those most important aspects of the system were implemented, I
continued work on the interface and extension of the analysis process mostly
alone for organizational reasons.

I chose to use mostly standard UNIX command line tools for writing, testing and
debugging the code, although more advanced solutions like the Eclipse Java IDE
were also used - mostly for easier organization of the work with the different
frameworks\footnote{Especially UIMA which comes with a number
